Along-Track Acceleration of Tropical Cyclones: A Proxy For Extratropical Interactions

### 2020-09-29 paper/mm.tex
update

%================================================================================================================
%================================================================================================================
%All Tables
%================================================================================================================

\begin{table*}[t]
  \caption{Speed (km hr$^{-1}$), tangential and curvature acceleration (km hr$^{-1}$ day$^{-1}$ ) of Atlantic TCs
   in the IBTRaCs database as a function of latitude. Storm instances classified as ET or NR have been excluded.
   N refers to number of 3-hourly track positions in each latitude-bin over the period 1966--2019. }
\begin{tabular}{|cc|ccc|ccc|ccc|}
\hline
& & \multicolumn{3}{|c|}{Speed} & \multicolumn{3}{c|}{Tang. Accel} & \multicolumn{3}{c|}{Curv. Accel}\\
\hline
Latitude & N & Mean & Median & Std Dev. & Mean & Median &  Std Dev.& Mean & Median & Std Dev.\\
	  5--15 &  5870 & 23.53 &  23.4 &   9.4 &  0.18 &   0.0 &  14.7 & 11.65 &   8.2 &  13.1 \\
	 10--20 & 13087 & 21.10 &  20.6 &   9.3 & -0.13 &  -0.0 &  15.3 & 12.29 &   8.5 &  13.3 \\
	 15--25 & 13656 & 18.66 &  18.1 &   8.6 &  0.26 &  -0.0 &  16.0 & 13.90 &   9.4 &  15.6 \\
	 20--30 & 13074 & 17.21 &  16.4 &   8.6 &  1.40 &   0.4 &  17.1 & 16.48 &  11.2 &  19.0 \\
	 25--35 & 13905 & 17.74 &  16.2 &  10.2 &  2.74 &   1.3 &  19.7 & 18.04 &  12.2 &  20.6 \\
	 30--40 & 10815 & 21.37 &  18.6 &  13.5 &  5.33 &   3.0 &  22.8 & 19.34 &  13.4 &  21.0 \\
	 35--45 &  5272 & 29.41 &  26.7 &  18.0 &  8.27 &   4.8 &  27.4 & 22.41 &  15.8 &  22.9 \\
	 40--50 &  1607 & 42.37 &  41.0 &  20.8 &  8.75 &   6.4 &  34.9 & 28.45 &  19.9 &  29.0 \\
	 45--55 &   329 & 55.69 &  53.9 &  19.4 &  6.81 &   6.3 &  37.8 & 36.50 &  25.9 &  38.9 \\
\bottomhline
\end{tabular}
%\belowtable{} % Table Footnotes
\label{tab:ATLSA}
\end{table*}
%==================================================================================

\begin{table*}[t]
  \caption{Trends in Speed (km hr$^{-1}$ year$^{-1}$) of Atlantic. All storms refers to all instances of a
    system recorded in the IBTraCs. ET refers to storm ntaure designated as extratropical, while NR refers to instances
    when the storm nature was not recorded. }

\begin{tabular}{|c|cccc|cccc|}
\hline
& \multicolumn{4}{|c|}{1966--2019}& \multicolumn{4}{|c|}{1949--2019}\\
& \multicolumn{2}{c}{LR} & \multicolumn{2}{c|}{MK-TS}& \multicolumn{2}{c}{LR} & \multicolumn{2}{c|}{MK-TS}\\
& Trend & P-value & Trend & P-value & Trend & P-value & Trend & P-value\\
\hline
Atlantic   &  0.029 & 0.19 &  0.028 & 0.15  & -0.016 & 0.28 & -0.016 & 0.32\\
(All storms) & & & & & & & &  \\
\hline
Atlantic  & -0.007 & 0.70 & -0.008 & 0.62 & -0.004 & 0.77 & -0.007 & 0.48\\
(Excluding ET,NR)  & & & & & & & &  \\
\hline
W. Pacific &  0.005 & 0.67 & -0.003 & 0.88 & \bf{-0.023} & < .01 & \bf{-0.027} & <.01\\
(All storms) & & & & & & & &  \\
\hline
\end{tabular}
%\belowtable{} % Table Footnotes
\label{tab:ATLSA}
\end{table*}

%==================================================================================
%==================================================================================

@@

%================================================================================================================
%All Figures
%================================================================================================================

%========================================================
%Figure 1
%========================================================

@@

%========================================================
%Figure 1
%========================================================

\begin{figure*}[t]
  \centering
    \includegraphics[width=.9\textwidth]{distribution_NA.png}
    \caption{Distribution of (a) Speed; (b) Tangential acceleration and (c) Curvature acceleration of
     Atlantic TCs as a function of latitude. Data from 1966--2019 was binned within 10$^o$-wide overlapping
     latitude bins. Statistics shown are: median (horizontal line within the box), mean (dot), and 10th,
     25th, 75th and 90th percentiles.}
  \label{fig:distNA}
\end{figure*}

@@

%========================================================
%Figure 1
%========================================================

\begin{figure*}[t]
\includegraphics[width=7cm]{altl_speed_trend.png}
\caption{Annual-mean speed of Atlantic storms, along with the linear trend. The purple curve is for all storms while the green curve excludes instances when
the storm was classified as ET or NR.}\label{fig:atl_speed}
\end{figure*}
%========================================================

@@

%\begin{figure}[ht]
%  \centering
%    \includegraphics[width=.7\textwidth]{distributionWP.png}
%  \caption{}
%  \label{fig:distWP}
%\end{figure}

@@

\end{document}

>>>>

%========================================================
%========================================================
%All Tables
%========================================================

\begin{table*}[t]
\caption{Speed (km hr$^{-1}$), tangential and curvature acceleration  (km hr$^{-1}$ day$^{-1}$ ) of all Atlantic non-ET storms as a function of latitude: N refers to number of 3-hourly track positions in each latitude-bin over the period 1966--2019. Storm positions corresponding to 
nature labels "ET" and "NR" were excluded.}

\begin{tabular}{|cc|ccc|ccc|ccc|}
\hline
& & \multicolumn{3}{|c|}{Speed} & \multicolumn{3}{c|}{Tang. Accel} & \multicolumn{3}{c|}{Curv. Accel}\\
\hline
Latitude & N & Mean & Median & Std Dev. & Mean & Median &  Std Dev.& Mean & Median & Std Dev.\\
	  5--15 &  5870 & 23.53 &  23.4 &   9.4 &  0.18 &   0.0 &  14.7 & 11.65 &   8.2 &  13.1 \\
	 10--20 & 13087 & 21.10 &  20.6 &   9.3 & -0.13 &  -0.0 &  15.3 & 12.29 &   8.5 &  13.3 \\
	 15--25 & 13656 & 18.66 &  18.1 &   8.6 &  0.26 &  -0.0 &  16.0 & 13.90 &   9.4 &  15.6 \\
	 20--30 & 13074 & 17.21 &  16.4 &   8.6 &  1.40 &   0.4 &  17.1 & 16.48 &  11.2 &  19.0 \\
	 25--35 & 13905 & 17.74 &  16.2 &  10.2 &  2.74 &   1.3 &  19.7 & 18.04 &  12.2 &  20.6 \\
	 30--40 & 10815 & 21.37 &  18.6 &  13.5 &  5.33 &   3.0 &  22.8 & 19.34 &  13.4 &  21.0 \\
	 35--45 &  5272 & 29.41 &  26.7 &  18.0 &  8.27 &   4.8 &  27.4 & 22.41 &  15.8 &  22.9 \\
	 40--50 &  1607 & 42.37 &  41.0 &  20.8 &  8.75 &   6.4 &  34.9 & 28.45 &  19.9 &  29.0 \\
	 45--55 &   329 & 55.69 &  53.9 &  19.4 &  6.81 &   6.3 &  37.8 & 36.50 &  25.9 &  38.9 \\
\bottomhline
\end{tabular}
%\belowtable{} % Table Footnotes
\label{tab:ATLSA}
\end{table*}
%==================================================================================

\begin{table*}[t]
\caption{Trends in Speed (km hr$^{-1}$ year$^{-1}$) of Atlantic.}

\begin{tabular}{|c|cccc|cccc|}
\hline
& \multicolumn{4}{|c|}{1966--2019}& \multicolumn{4}{|c|}{1949--2019}\\
& \multicolumn{2}{c}{LR} & \multicolumn{2}{c|}{MK-TS}& \multicolumn{2}{c}{LR} & \multicolumn{2}{c|}{MK-TS}\\
& Trend & P-value & Trend & P-value & Trend & P-value & Trend & P-value\\
\hline
Atlantic (No ET,NR)  & -0.007 & 0.70 & -0.008 & 0.62 & -0.004 & 0.77 & -0.007 & 0.48\\
\hline

Atlantic (All) &  0.029 & 0.19 &  0.028 & 0.15  & -0.016 & 0.28 & -0.016 & 0.32\\

\hline

W. Pacific (All) &  0.005 & 0.67 & -0.003 & 0.88 & \bf{-0.023} & < .01 & \bf{-0.027} & <.01\\

\hline

\end{tabular}
%\belowtable{} % Table Footnotes
\label{tab:ATLSA}
\end{table*}

%==================================================================================

\begin{table*}[t]
\caption{Trends in tangential acceleration (km hr$^{-1}$ day$^{-1}$ year$^{-1}$) of Atlantic.}

\begin{tabular}{|c|cccc|cccc|}
\hline
& \multicolumn{4}{|c|}{1966--2019}& \multicolumn{4}{|c|}{1949--2019}\\
& \multicolumn{2}{c}{LR} & \multicolumn{2}{c|}{MK-TS}& \multicolumn{2}{c}{LR} & \multicolumn{2}{c|}{MK-TS}\\
& Trend & P-value & Trend & P-value & Trend & P-value & Trend & P-value\\
\hline
Atlantic (No ET,NR)  & -0.007 & 0.70 & -0.008 & 0.62 & -0.004 & 0.77 & -0.007 & 0.48\\
\hline

Atlantic (All) &  0.029 & 0.19 &  0.028 & 0.15  & -0.016 & 0.28 & -0.016 & 0.32\\

\hline

W. Pacific (All) &  0.005 & 0.67 & -0.003 & 0.88 & \bf{-0.023} & < .01 & \bf{-0.027} & <.01\\

\hline

\end{tabular}
%\belowtable{} % Table Footnotes
\label{tab:ATLSA}
\end{table*}

%==================================================================================

@@

%========================================================
%All Figures
%========================================================
%Figure 1
%========================================================

@@

\begin{figure}[ht]
  \centering
    \includegraphics[width=.9\textwidth]{distributionNA.png}
  \caption{}
  \label{fig:distNA}
\end{figure}

@@

@@

\begin{figure}[ht]
  \centering
    \includegraphics[width=.7\textwidth]{distributionWP.png}
  \caption{}
  \label{fig:distWP}
\end{figure}

@@

%===================================================
\begin{table*}[t]
\caption{Trend in Speed (km hr$^{-1}$)}

\begin{tabular}{c|cc|cc|cc|cc|}
\tophline
1966--2019 & -0.019 & 0.22 & -0.021 & 0.21

\bottomhline
\end{tabular}
%\belowtable{} % Table Footnotes
\label{tab:WPSA}
\end{table*}

%1949--2016 
%1949--2019
\end{document}
